---
title: "Exploratory Analysis"
output: html_document
---

## Project title

Give your project a concise, interesting title that summarizes the entirety of your project

### Authors

Names of your team members

### Date

Winter 2022

### Abstract

No more than three sentences that summarize your project. Focus on the very most important aspects. For example: (1) "Our main question is .... This question is important because .... To address the question, we will ...." (2) "We are concerned with ..., because .... To address this concern, we plan to ...." (3) "Consider that .... This is important because .... Accordingly, we plan to ...."

### Keywords

3-5 keywords that summarize your project.
(e.g., "Keywords: human physiology; bicycle exercise; Gen Z; times-series data")

### Introduction  

Briefly introduce your project.  Include 3-5 research questions. What motivates the questions? Why are they important? (at least 200 words)

### Related Work  

Describe your topic and related work in this space. You must include 3 citations to related work (URLs to similar work, high quality articles from the popular press, research papers, etc. ) Please use a standard citation style of your choice. (at least 200 words)

### The Dataset

Where did you find the data? Please include a link to the data source  
Who collected the data?  
How was the data collected or generated?  
Why was the data collected?  
How many observations (rows) are in your data?  
How many features (columns) are in the data?  
What, if any, ethical questions or questions of power do you need to consider when working with this data?  
What are possible limitations or problems with this data?   (at least 200 words)

### Implications

Assuming you answer your research questions, briefly describe the expected or possible implications for technologists, designers, and policymakers. (at least 150 words)

### Limitations & Challenges
What challenges or limitations might you need to address with your project idea more broadly? Briefly discuss. (at least 150 words)

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

### Table

Include a table of aggregate information
Describe why you included the table and what information it reveals

### Chart 1

Include a chart

Describe why you chose this chart and what information it reveals

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart1_example.R")}
```

### Chart 2

Describe why you chose this chart and what information it reveals
I chose a bar chart to show the frequency of age in the dataset since bar chart is a useful chart for showing the distribution or frequency of a categorical variable.

The information revealed by this chart is the number of instances that each age appeared in the table This can help identify the most common and least common ages in the dataset, and provide insight into the age distribution of the data.

Besides, this chart can also be used to identify any trends or patterns in the age distribution. For example, if there is a large spike in the frequency of a particular age group, this may indicate a specific demographic that is overrepresented in the dataset.

Therefore, a bar chart is a simple and effective way to show the frequency of age in the dataset, and can help provide insight into the age distribution of the data.
``````{r, echo = FALSE, code = readLines("chart2.R")}
```

### Chart 3

Include a chart

Describe why you chose this chart and what information it reveals
