---
title: "Exploratory Analysis"
output: html_document
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# source all R files
source("Chart1.R")
source("Chart3.R")
```

## Project title

Break the Gender & Age Bias in Traffic

### Authors

Aaron He, 

### Date

Winter 2023

### Abstract

No more than three sentences that summarize your project. Focus on the very most important aspects. For example: (1) "Our main question is .... This question is important because .... To address the question, we will ...." (2) "We are concerned with ..., because .... To address this concern, we plan to ...." (3) "Consider that .... This is important because .... Accordingly, we plan to ...."

### Keywords

3-5 keywords that summarize your project.
(e.g., "Keywords: human physiology; bicycle exercise; Gen Z; times-series data")

### Introduction  

Briefly introduce your project.  Include 3-5 research questions. What motivates the questions? Why are they important? (at least 200 words)

### Related Work  

Describe your topic and related work in this space. You must include 3 citations to related work (URLs to similar work, high quality articles from the popular press, research papers, etc. ) Please use a standard citation style of your choice. (at least 200 words)

### The Dataset

Where did you find the data? Please include a link to the data source  
Who collected the data?  
How was the data collected or generated?  
Why was the data collected?  
How many observations (rows) are in your data?  
How many features (columns) are in the data?  
What, if any, ethical questions or questions of power do you need to consider when working with this data?  
What are possible limitations or problems with this data?   (at least 200 words)

### Implications

Assuming you answer your research questions, briefly describe the expected or possible implications for technologists, designers, and policymakers. (at least 150 words)

### Limitations & Challenges
What challenges or limitations might you need to address with your project idea more broadly? Briefly discuss. (at least 150 words)

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

setwd("/Users/aaron/Desktop")
np_data <- read.csv("Info201 Dataset.csv")
### Table


Include a table of aggregate information

Describe why you included the table and what information it reveals

### Chart 1

Include a chart

Describe why you chose this chart and what information it reveals

The scatterplot can be in providing additional information based on the dataset. Specifically, the chart provides more detailed information about the relationship between gender and the number of car accidents.

The table depicted that there were a total number of collisions for each gender group, which may provide additional insight into the relationship between gender and car accidents. In detail, the group of male is easier to have the car accidents.

Overall, including the table helps to provide a more complete picture of the data and can provide additional insight into the relationship between gender and car accidents.


```{r, echo = FALSE, code = readLines("Chart1.R")}
C1
```

### Chart 2

Include a chart

Describe why you chose this chart and what information it reveals

### Chart 3

Include a chart

Describe why you chose this chart and what information it reveals

This chart provides insight into the relationship between gender and degree of injury, and can help identify patterns or trends in the injury data. We filter out the data under gender "Not Reported".

The stacked bar chart with percentage shows the proportion of different injury level within each gender. As shown by graph, the percentage of having injury level between 0-2.5 are mostly same for both gender. But for the percentage of having injury level 4.0-6.0, male cases are greatly larger than female's one. So we can state that, male are in a higher risk of getting seriously injured. 

```{r, echo = FALSE, code = readLines("Chart3.R")}
C3
```
